Ornaments as indicators of social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-08-20 analysis/paper/paper.Rmd
shorten some sentences

Prior to contact with the Europeans in the early 17th century, Taiwan had been involved in both regional and long-distance East and Southeast Asian trade systems since the 10th century, and encountered large waves of Han Chinese immigration after 17th century when Taiwan was incorporated into the territories of Qing Dynasty of China [@Liu2017; @Andrade2007, ch. 11]. The exchange network in northern Taiwan was influenced by long-distance trade between Fuzhou or Quanzhou in China and Ryukyu in Japan since the 15th century due to its location on shipping routes [@Chen2005]. This intensified in the 17th century with the arrival of the Europeans and their trade goods [@Wang2007].

>>>>

Prior to contact with the Europeans in the early 17th century, Taiwan had been involved in both regional and long-distance East and Southeast Asian trade systems since the 10th century. Taiwan encountered large waves of Han Chinese immigration after 17th century when Taiwan was incorporated into the territories of Qing Dynasty of China [@Liu2017; @Andrade2007, ch. 11]. The exchange network in northern Taiwan was influenced by long-distance trade between Fuzhou or Quanzhou in China and Ryukyu in Japan since the 15th century due to its location on shipping routes [@Chen2005]. This intensified in the 17th century with the arrival of the Europeans and their trade goods [@Wang2007].
